---
title: "Pollyvoter"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


## 1. concept

The idea is to create a general object (list) which contains all necessary information. This created object will get the object class "pollyvote".   
Another special feature is to save only the most important characteristics of the object (e.g. poll data, election results, aggregation functions, ...). Other 
calculated results like predictions or error calculations will not be saved in pollyvote the object. 


## 2. functionalities

The `pollyvote-package` contains the following functionalities:

- save election predictions from different sources and source types    
- save election results      
- predict election results with aggregated election prediction from different sources    
- results in graphical form       
- error calculation    
- define own aggregation and error calculation functions


## 3. examples for application


This section shows the most important functionalities of `pollyvote`-package using
examples. 


```{r, echo = FALSE, warning = FALSE, message = FALSE}

library(devtools)
load_all()

```

### create empty pollyvote container

With function `create_pollyvote` you can create an empty pollyvote object. It is also possible to define permitted values for the respective column of the data of this pollyvote object.

```{r}

pv = create_pollyvote(perm_countries = "D")

```


### add data to pollyvote

Use `add_data` to include election data. Additional arguments allow to specify
information about data e.g. country, region, source type. 

```{r}

  data("polls_individual")
  pv = add_data(pv, newdata = polls_individual, country = "D", region = "national", 
                source_type = "poll", election = "BTW")
  head(pv$data)
  
```



### add election results

Use `add_election_result` to add election results. Election results are necessary for error calculation.

```{r}

data("election_result")
pv = add_election_result(pv, "BTW", election_result, date = "2013-09-22")
head(pv$election_result)

```


### predictions


```{r}

pred <- predict(pv, "pollyvote")
head(pred, 20)

```


### plot predictions

Apply `plot` function to create a graphical representation of prediction. Since prediction results weren't stored, a prediction method specification is required. 

```{r}

plot(pv, prediction_method = "pollyvote")

```


### error calculation

The calculated error is the absolute difference between election results and predicted values. 

```{r}

error_calc_pred <- error_calc(pv, "prediction_election", 
                              prediction = "pollyvote", election = "BTW")
error_calc_pred[1:10, c("party", "percent", "percent.true", "government",
                        "error")]

```



### error calculation with confidence interval

Confidence interval is just a special case of error calculation. Use an error calculation function with a `ci = TRUE` and `alpha value`.

```{r}

error_pred_conf_int <- error_calc(pv, "prediction_election", 
                                  prediction = "pollyvote", election = "BTW",
                                  ci = TRUE, alpha = 0.3)
error_pred_conf_int[1:10, c("party", "percent", "percent.true","error",
                            "mean_error", "ci_lower", "ci_upper")]

```


### save as .csv file

To save predictions or error calculations use function `write.pollyvote`. It is important to specify either the prediction (argument `prediction`) or the error calculation method (argument `error_calculation`). 

```{r}

write.pollyvote(pv, file = "pred.csv", method = "write.table", 
                prediction = "pollyvote")
  
write.pollyvote(pv, file = "error_calc.csv", method = "write.table",
                error_calculation = "prediction_election")

```


